 Total Team Spending and Profitability Results in a Higher League Ranking in the English Premier League

### 2024-04-19 paper/paper.qmd
Committing all changes 04-19-2024 @1:56am.

```{r}
#| echo: false
#| warning: false

@@

```{r}
#| label: tbl-7
#| tbl-cap: Summary of Linear Model Coefficients.
#| echo: false
#| warning: false

model_summary <- summary(model)
coefs <- data.frame(
  Term = rownames(model_summary$coefficients),
  Estimate = model_summary$coefficients[, "Estimate"],
  StdError = model_summary$coefficients[, "Std. Error"],
  tValue = model_summary$coefficients[, "t value"],
  Pr = model_summary$coefficients[, "Pr(>|t|)"]
)
kable(coefs, caption = "Summary of Linear Model Coefficients", format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

>>>>

@tbl-7 shows the table of the coefficients after running the linear model summary.
```{r}
#| echo: false
#| warning: false
#| results: 'hide'

@@

```{r}
#| label: tbl-7
#| tbl-cap: Summary of Linear Model Coefficients
#| echo: false
#| warning: false

model_summary <- summary(model)
coefs <- data.frame(
  Estimate = model_summary$coefficients[, "Estimate"],
  StdError = model_summary$coefficients[, "Std. Error"],
  tValue = model_summary$coefficients[, "t value"],
  Pr = model_summary$coefficients[, "Pr(>|t|)"]
)

kable(coefs, format = "latex", booktabs = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)

@@

Note:
Residuals:
     Min       1Q   Median       3Q      Max 
-10.8121  -6.0644  -0.9837   5.1376  15.9644

Residual standard error: 8.261 on 16 degrees of freedom
Multiple R-squared:  0.8057,	Adjusted R-squared:  0.7693 
F-statistic: 22.12 on 3 and 16 DF,  p-value: 6.159e-06
